### 2021-04-08 submission/manuscript.Rmd
Rough draft of fig 4 legend, pval and R-sq still to be included

Sarah Tomkovich^1, Ana Taylor, Jacob Kingg, Joanna Colovas, Lucas Bishop, Kathryn McBride, Sonya Royzenblat, Nicholas A. Lesniak, Ingrid L. Bergin^2, Patrick D. Schloss^1$\dagger$^

@@

@@

\includegraphics{figure_4.pdf}
**Figure 4. 1-day PEG treatment renders mice susceptible to transient *C. difficile* colonization.** A. 
\newpage

>>>>

Sarah Tomkovich^1, Ana Taylor, Jacob King, Joanna Colovas, Lucas Bishop, Kathryn McBride, Sonya Royzenblat, Nicholas A. Lesniak, Ingrid L. Bergin^2, Patrick D. Schloss^1$\dagger$^

@@

fig_4_pval = 1
fig_4_rsq = 1

@@

\includegraphics{figure_4.pdf}
**Figure 4. 1-day PEG treatment renders mice susceptible to transient *C. difficile* colonization.** A. Setup of the experimental timeline for the 1-day PEG treated subset of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint) via several dilutions. The black dotted line represents the limit of detection for the first serial dilution. Asterisks indicate timepoints where the CFU/gram was siginificantly different between groups using the Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple timepoints. C. Principle Coordinate Analysis plot of the groups over time with the alpha representating the same time scale as in panel D (P = `r fig_4_pval` R^2^ = `r fig_4_rsq`). D. Shannon Diveristy Index of the groups over time. Only days with samples from all groups are shown. Samples for some mice were difficult to obtain 
due to the laxative treatment. The alpha scale follows accordingly with the timeline. E. Line plots of relative percent abundance of selected genera over time. Only days with samples from all groups shown. The gray line represents the limit of detection.

### 2021-04-08 submission/manuscript.tex
Demo rmarkdown with Ana
Rough draft of fig 4 legend, pval and R-sq still to be included

Sarah Tomkovich\^{}1, Ana Taylor, Jacob Kingg, Joanna Colovas, Lucas
Bishop, Kathryn McBride, Sonya Royzenblat, Nicholas A. Lesniak, Ingrid
L. Bergin\^{}2, Patrick D. Schloss\textsuperscript{1\(\dagger\)}

@@

\includegraphics{figure_1.pdf} \textbf{Figure 1. 5-day PEG treatment
prolongs susceptibility and mice become persistently colonized with
\emph{C. difficile}.} A. Setup of the experimental timeline for subset
of experiments with 5-day PEG treated mice. B. Weight change from
baseline weight in groups after treatment with PEG and/or clindamycin,
followed by \emph{C. difficile} challenge. C. \emph{C. difficile}
CFU/gram stool measured over time (N =
4-\texttt{(insert\ variable\ name)} mice per timepoint) via serial
dilutions. The black line represents the limit of detection for the
first serial dilution. CFU quantification data was not available for
each mouse due to stool sampling difficulties (particularly the day the
mice came off of the PEG treatment) or early deaths. Lines represent the
median for each source and circles represent individual mouse samples.
Asterisks indicate timepoints where the weight change or CFU/g was
significantly different between groups by the Kruskal-Wallis test with
Benjamini-Hochberg correction for testing multiple timepoints. \newpage

@@

\includegraphics{figure_4.pdf} \textbf{Figure 4. 1-day PEG treatment
renders mice susceptible to transient \emph{C. difficile} colonization.}
A. \newpage

>>>>

Sarah Tomkovich\^{}1, Ana Taylor, Jacob King, Joanna Colovas, Lucas
Bishop, Kathryn McBride, Sonya Royzenblat, Nicholas A. Lesniak, Ingrid
L. Bergin\^{}2, Patrick D. Schloss\textsuperscript{1\(\dagger\)}

@@

\includegraphics{figure_1.pdf}

\textbf{Figure 1. 5-day PEG treatment prolongs susceptibility and mice
become persistently colonized with \emph{C. difficile}.} A. Setup of the
experimental timeline for subset of experiments with 5-day PEG treated
mice. B. Weight change from baseline weight in groups after treatment
with PEG and/or clindamycin, followed by \emph{C. difficile} challenge.
C. \emph{C. difficile} CFU/gram stool measured over time (N =
4-\texttt{(insert\ variable\ name)} mice per timepoint) via serial
dilutions. The black line represents the limit of detection for the
first serial dilution. CFU quantification data was not available for
each mouse due to stool sampling difficulties (particularly the day the
mice came off of the PEG treatment) or early deaths. Lines represent the
median for each source and circles represent individual mouse samples.
Asterisks indicate timepoints where the weight change or CFU/g was
significantly different between groups by the Kruskal-Wallis test with
Benjamini-Hochberg correction for testing multiple timepoints. \newpage

@@

\includegraphics{figure_4.pdf} \textbf{Figure 4. 1-day PEG treatment
renders mice susceptible to transient \emph{C. difficile} colonization.}
A. Setup of the experimental timeline for the 1-day PEG treated subset
of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint)
via several dilutions. The black dotted line represents the limit of
detection for the first serial dilution. Asterisks indicate timepoints
where the CFU/gram was siginificantly different between groups using the
Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple
timepoints. C. Principle Coordinate Analysis plot of the groups over
time with the alpha representating the same time scale as in panel D (P
= 1 R\textsuperscript{2} = 1). D. Shannon Diveristy Index of the groups
over time. Only days with samples from all groups are shown. Samples for
some mice were difficult to obtain due to the laxative treatment. The
alpha scale follows accordingly with the timeline. E. Line plots of
relative percent abundance of selected genera over time. Only days with
samples from all groups shown. The gray line represents the limit of
detection.
